---
title: "last lab 206"
author: "Amelia Ritger"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(corrplot)
library(beepr)
library(praise)
library(stargazer)
library(sf)
library(gganimate)
library(transformr)
```

## Objectives:

- Multiple linear regression
- Our first map with sf and ggplot

### Part 1. Multiple linear regression : SLO home prices

```{r}
homes <- read_csv("slo_homes.csv") %>%
  clean_names()

beep(2)

praise()
names(praise_parts)
praise("You are totally ${adjective}! Super ${EXCLAMATION}")
```

```{r}
homes_sub <- homes %>%
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande"))
beep(3)
```

Are there correlations between variables that we'd consider while trying to model home price?

```{r}
homes_cor <- cor(homes_sub[2:5])

corrplot(homes_cor,
         method="ellipse",
         type="upper")
```

```{r}
ggplot(data=homes_sub, aes(x=sq_ft, y=price)) +
  geom_point()
```

Let's start with a complete model (includes city, bedrooms, bathrooms, sq_ft, and sale status):

```{r}
homes_lm <- lm(price ~ city + bedrooms + bathrooms +sq_ft + status, data=homes_sub)
summary(homes_lm)
#home price = 1834130 - 167396(Atasc) + 31018(SLO) - 161645(bedrooms)...
#with all else being equal, this tells us we expect a home in Atascadero to be $167k less than in Arroyo Grande (or $31k more in SLO)
#bedrooms variable is concerning... why would a home price decrease by $161k with every additional bedroom?
```

Now let's try another version of the model:
Just using sq_ft as a measure of home size

```{r}
homes_lm2 <- lm(price ~ city + sq_ft + status, data=homes_sub)
praise()
beep(6)
summary(homes_lm2) #good example here why interpreting intercept is not interesting/difficult
```

AIC

```{r}
AIC(homes_lm) #better model fit...but obviously don't rely only on AIC (also because model 1 doesn't make total sense)
AIC(homes_lm2)
```

### Now: check assumptions for normality and homoscedasticity
```{r}
plot(homes_lm2)
# Yep, looks like the assumption of constant variances of residuals (homoscedasticity) is OK from residuals vs fitted plot
# normality of residuals from q-q plot (good)
praise()
```

Make a nice regression table:
```{r, results='asis'}
stargazer(homes_lm2, type="html")
```

Let's make some predictions for home price based on a new data frame of home characteristics.

Make sure that the variables we create for the new data match the variables that the model will be looking for to make new predictions.

```{r}
new_df <- data.frame(
  city = rep(c("San Luis Obispo", "Arroyo Grande", "Atascadero"), each=10),
  sq_ft = rep(seq(1000, 5000, length=10)),
  status = "Regular"
)
```

Now we'll make predictions for home price based on that new data:
```{r}
predict_df <- predict(homes_lm2, newdata=new_df) #what is the predicted home value given the model and sq_ft I specified?

#bind together the new df with the predictions
full_data <- data.frame(new_df, predict_df)
```

Now plot in ggplot2:
```{r}
ggplot() +
  geom_point(data=homes_sub, aes(x=sq_ft, y=price, color=city, pch=city)) +
  geom_line(data=full_data, aes(x=sq_ft, y=predict_df, color=city)) +
  scale_color_manual(values=c("orange", "magenta", "black")) +
  theme_bw()
```
 
### Our first map (thanks `{sf}` package!)

`sf`: by Edzer Pebesma
Great beacuse: sticky geometries
*With sticky geometries, you can wrangle columns variables whatever and the geometry will stick to it!*


```{r}
dams <- read_csv("ca_dams.csv") %>%
  clean_names() %>%
  drop_na(latitude) %>%
  drop_na(longitude) %>%
  drop_na(year_completed)

#Convert our data from to an sf object using st_as_sf
dams_sf <- st_as_sf(dams, coords = c("longitude", "latitude"))
class(dams_sf)
st_crs(dams_sf) <- 4326 # telling R what coordinate system to use
plot(dams_sf) # dam, plot() is powerful!
```

Read in the California border polygon data:
```{r}
ca_border <- read_sf(here::here("ca_state_border"), layer="CA_State_Tiger2016")
plot(ca_border)
```

Now let's plot them together with ggplot2:
```{r}
ggplot() +
  geom_sf(data=ca_border, fill="darkgreen", color="darkgreen", alpha=0.2) +
  geom_sf(data=dams_sf, color="blue", size=1, alpha=0.4) +
  theme_void()
```

Now let's animate it with gganimate
```{r}
ggplot() +
  geom_sf(data=ca_border, fill="darkgreen", color="darkgreen", alpha=0.2) +
  geom_sf(data=dams_sf, color="blue", size=1, alpha=0.4) +
  theme_void() +
  labs(title='Year:{round(frame_time,0)}') +
  gganimate::transition_time(year_completed) +
  shadow_mark()

beep(2)
```



